$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-03 paper/paper.tex
Move ^2 up to where multiplicities are introduced
Small clarification

Linear, gradual and shared types are all defined as an instance of our usage algebra.
Their use in typing derivations is illustrated in \autoref{example-derivations}.

@@

\begin{note}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\Usage_{idx}^{\func{2}}$ to stand for a $\Usage_{idx} \times \Usage_{idx}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted element-wise.
  Henceforth, we use $\lz$ to denote the pair $(0 \comma 0)$, $\li$ for the pair $(1 \comma 0)$, $\lo$ for $(0 \comma 1)$ and $\lio$ for $(1 \comma 1)$, borrowing from the linear \picalc{} notation \cite{KPT96,Sangio01}.
\end{note}

>>>>

\begin{note}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \times \type{C}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted element-wise.
  Henceforth, we use $\lz$ to denote the pair $(0 \comma 0)$, $\li$ for the pair $(1 \comma 0)$, $\lo$ for $(0 \comma 1)$ and $\lio$ for $(1 \comma 1)$, borrowing from the linear \picalc{} notation \cite{KPT96,Sangio01}.
\end{note}

Linear, gradual and shared types (identified by a value in \Idx) are all defined as an instance of our usage algebra.
Their use in typing derivations is illustrated in \autoref{example-derivations}.

@@
